---
title: "R Notebook"
output: html_notebook
---
### 4.1
```{r}
typeof(c("John", "Mary"))
typeof(c(2, 3.1412))
typeof(c(TRUE, TRUE, F))
```

```{r}
class(c("John", "Mary")) #categorize as character class
class(c(2, 3.1412))
class(c(TRUE, TRUE, F))
```

**class** is a categorisation method that categorises different values based on **what we can do with those valuess**

real life example
* type : man and woman
*class : different based on skills (plumber class, teacher class) based on what those people can do

***

```{r}
#date time information
dataTimeinfo <- "2021-01-01 12:03:33"
typeof(dateTimeInfo)
```

```{r}
class(dataTimeinfo)
```

```{r}
"2021-01-01 12:03:33" + "20 seconds"
```

```{r}
dataTimeinfo + 20
#character class value + 20
```

we can use proper parsing function to teach R understand a data time value is more than a character--teach R understand a class called date/time

```{r}
dateTimeInfo2 <- lubridate::ymd_hms("2021-01-01 12:03:33") #UTC is a timezone 
class(dateTimeInfo2) #ct calender time #t tipme hour minute second #posix universal standard how we write things
```

lubridate::ymd_hms is a parsing function to teach R understand date and time

```{r}
dateTimeInfo2 + lubridate::seconds(20)
```
type : how we store **raw** info
class : what R can do with different information

### 4.2

```{r}
commonClasses <- list()
```
 *declare then add methid to create vector

```{r}
# save three different atomic vectors
commonClasses$character <- c("John", "Mary", "Bill")
commonClasses$numeric <- c(2.3, 4, 7)
commonClasses$logical <- c(TRUE, T, F, FALSE)
```

```{r}
# check each atomic vector class
class(commonClasses$character) # name call on commonClasses to get its value then retrieve the element value whose element name is "character"

class(commonClasses$numeric)
class(commonClasses$logical)
```

```{r}
bloodTypes <- c("AB", "AB", "A", "B", "A", "A", "B", "O", "O", "AB") #categorical data
```

factor can make R understand categorical data

```{r}
bloodTypes_fct <- 
  factor(bloodTypes)
# after name call on blood type
# bloodTypes_fct <- factor("AB", "AB", "A", "B", "A", "A", "B", "O", "O", "AB")
```

```{r}
class(bloodTypes)
class(bloodTypes_fct)
```

```{r}
table(bloodTypes_fct) # supposed only work with factor data
```

```{r}
levels(bloodTypes_fct)
```

```{r}
levels(bloodTypes) # NULL because blood type is not a factor
```

```{r}
bloodTypes_fct_levelsSetup <- 
  factor(bloodTypes, levels=c("A", "B", "O", "AB")) #setbup story sequance of level
```

```{r}
class(bloodTypes_fct_levelsSetup)
```

```{r}
table(bloodTypes_fct_levelsSetup)
```

***

```{r}
household_income <- c("low income", "low income", "middle income", "low income", "high income", "middle income", "high income", "high income", "middle income", "middle income")
```
*low income < middle income < high income

```{r}
household_income_fct <- 
  factor(household_income) # parsing factor = let know this is factor
levels(household_income_fct) # start from high
```

if you want it to start from low so

```{r}
household_income_fct_levelsSetup <-
  factor(household_income, levels = c("low income", "middle income", "high income"))
levels(household_income_fct_levelsSetup)
```

```{r}
table(household_income_fct_levelsSetup)
```

```{r}
household_income_fct_levelsSetup[[1]]
```

```{r}
household_income_fct_levelsSetup[[1]] < "middle income"
```
* human would say yes, it is true.

```{r}
household_income_fct_levelsSetup_ordered[[1]] = "low income"
```

```{r}
household_income_fct_levelsSetup_ordered[[1]] < "middle income"
```


```{r}
household_income_fct_levelsSetup_ordered <-
  factor(
    household_income, 
    levels = c("low income", "middle income", "high income"),
    ordered = TRUE # is levels ordered? from smallest to largest
    )
```

```{r}
class(household_income_fct_levelsSetup_ordered)
```

```{r}
class(household_income_fct)
class(household_income_fct_levelsSetup)
```

```{r}
commonClasses$ordered_factor <- household_income_fct_levelsSetup_ordered
class(commonClasses$ordered_factor)
```


```{r}
commonClasses$factor <- bloodTypes_fct_levelsSetup
class(commonClasses$factor)
# factor parsed data has factor class
```


