##4.3.1

```{r}
c(2, 5, 7) + 3 # work
list(2, 5, 7) + 3 # won't work so put class conversion first because class operation only works on atomic vector
```

```{r}
convert2numeric <- as.numeric(c("2", "5", "7")) 
convert2numeric + 3
```

```{r}
mylist <- list(2, 5, 7)
mylist[[1]] <- mylist[[1]]+3
mylist[[2]] <- mylist[[2]]+3
mylist[[3]] <- mylist[[3]]+3
print(mylist)
```

```{r}
unlist(mylist) + 3
```
unlist is to convert list to atominc vector
```{r}
examples <- list()
examples$unlist$source1 <-
  list("A", "B", "C")
examples$unlist$result1 <- 
  unlist(examples$unlist$source1)

print(examples$unlist$source1)
print(examples$unlist$result1)

class(examples$unlist$source1)
class(examples$unlist$result1)
```



```{r}
examples$unlist$source2 <- 
  list(
    list("A", "B", list("C")),
    list("D"),
    "E"
  )
examples$unlist$result2 <- 
  unlist(
    examples$unlist$source2
  )

print(examples$unlist$source2)
print(examples$unlist$result2)
class(examples$unlist$source2)
class(examples$unlist$result2)
```

```{r}
participations <- 
list('session 3',c("session 1", "session 2", "session 3"),'session 3',c("session 2", "session 1"),c("session 3", "session 1"),c("session 3", "session 2", "session 1"),'session 2','session 1',c("session 2", "session 1", "session 3"),c("session 3", "session 1", "session 2"))
```

```{r}
# sessions that 1st student attended
participations[[1]] 
# sessions that 2nd student attended
participations[[2]]
```

##4.3.2
!as.list(
  c("A", "B", "C")
)
```{r}
as.list(
  c("A", "B", "C")
) # not the same as 
list(c("A", "B", "C")
)

# element names will be preserved
as.list(
  c(name="John", spouse="Mary")
)
```

##4.3.3
```{r}
lgl <- c(TRUE, FALSE) #logical
num <- c(0.2, 3, 0) #numeric
```

```{r}
as.character(lgl) #same as 
c("TRUE", "FALSE")
as.character(num)
```

***
as.numeric
```{r}
tookRcourse <- c(TRUE, FALSE, TRUE, TRUE)
as.numeric(tookRcourse)
howManyTookR <- sum(
  as.numeric(tookRcourse)
)
print(howManyTookR)
```

```{r}
howManyTookR <- sum(tookRcourse)
print(howManyTookR)
```

```{r}
ming_guoDates <- c("1100822","1090723") # 民國100-8-22，民國109-7-23

# 民國1年 is 1911
westernDates <- 
  as.numeric(ming_guoDates) +
  19110000

westernDates 

lubridate::ymd(westernDates)
```

as logical :
any number is zero
```{r}
# on numeric vector
# tell us if the number is not zero
print(num)
as.logical(num)
```

who has a job
```{r}
# only person with a non-zero wage has a job
wage <- c(3000, 2000, 0, 1000)
haveJob <- as.logical(wage)
haveJob
```

Extended class’s value has a feature that it’s stored values (i.e. storage type) may be different from it’s printed values (i.e. what we see on name call or print).

For extended classes,

as.numeric() works on the type of storage of the extended class.

as.character() works on the print out of the extended class.

```{r}
fct <- factor(
  c('參','貮','貮','貮','壹','貮','參','貮','參','參'),
  levels=c('壹','貮','參')
  )

dt <- lubridate::ymd_hms(
  c('2012-08-25 19:36:00','2018-01-06 10:44:00','2010-03-08 00:56:00')
)
```

```{r}
print(fct)
as.character(fct)

typeof(fct)
as.numeric(fct) # the positions in levels
```










