##4.2.3

```{r}
lubridate::ymd(c("2021/10/30", "2021-10-30", "2021 October 30", "2021 Oct. 30"))
lubridate::ydm(c("2021/30/10", "2021-30-10", "2021 30 October", "2021 30 Oct."))
lubridate::mdy(c("10/30/2021", "10-30-2021", "October 30, 2021", "Oct. 30, 2021"))
lubridate::dmy(c("30/10/2021", "30-10-2021", "30 October, 2021", "30 Oct., 2021"))
```
what kind of type you are using
if ymd type use lubridate

```{r}
commonClasses <- list()
# save three different atomic vectors
commonClasses$character <- c("John", "Mary", "Bill")
commonClasses$numeric <- c(2.3, 4, 7)
commonClasses$logical <- c(TRUE, T, F, FALSE)
```

```{r}
# A parsed date data has Date class.
commonClasses$date <- lubridate::dmy(c("30/10/2021", "30-10-2021", "30 October, 2021", "30 Oct., 2021"))
class(commonClasses$date)
```

for time we have
hms: hour minute second
hm: hour minute
h: hour
depending on how accurate you are

for date we have the combination of (ymd, ydm, mdy, dmy)

```{r}
dateTime_taipei <- 
  lubridate::ymd_hms(
    c("2021/10/30 13:22:52", "2021-10-31 1:22:52PM"),
    tz = "Asia/Taipei")
dateTime_taipei
```

```{r}
dateTime_london <- 
  lubridate::mdy_hm(
    c("October 30, 2021, 23:10", "Oct. 30, 2021 11:10PM"),
    tz="Europe/London")
dateTime_london
```

```{r}
commonClasses$date_time <- c(
  dateTime_taipei,
  dateTime_london
)
class(commonClasses$date_time)
```

A parsed date/time data has classes POSIXct and POSIXt. We will call it date/time class.

POSIX (the Portable Operating System Interface) is a standard (標準化格式); ct refers to calendar time and t refers to time.

Here both dateTime_taipei and dateTime_london are of the same date/time class. So we can concatenate them to form an atomic vector (which is also a date/time class):
```{r}
c(dateTime_taipei, dateTime_london)
```

A single time zone will be used through out the data/time class vector:
```{r}
commonClasses$date_time
```

Once a date/time source value is parsed, R will understand its meaning and know how to convert it to different time zone through lubridate::with_tz():
```{r}
dateTime_london_atTaipei <-
  lubridate::with_tz(
    dateTime_london,
    tz="Asia/Taipei"
  )
dateTime_london
dateTime_london_atTaipei
```

Be aware that for R to convert time zone the time value must be parsed date/time class value. Never do the following:
```{r}
lubridate::with_tz(
  c("October 30, 2021, 23:10", "Oct. 30, 2021 1:10AM"),
  tz="Asia/Taipei"
)
```

##4.2.4
If the data set list is collected feature-by-feature so that
all the feature vectors have the same length.
and are named.
```{r}
survey_fbf <-
  list(
    age=c(54, 32, 28, 20), # age
    gender=c("male", "female", "female", "male"), # gender
    residence=c("north", "south", "east", "east"), # residence
    income=c(100, 25, NA, 77) # income
  )
```

```{r}
survey_df <-
  data.frame(
    survey_fbf
  )
```

```{r}
survey_df_1step <-
  data.frame(
    age=c(54, 32, 28, 20), # age
    gender=c("male", "female", "female", "male"), # gender
    residence=c("north", "south", "east", "east"), # residence
    income=c(100, 25, NA, 77) # income
  )
```

```{r}
# a parsed collection value will have data.frame class.
commonClasses$data_frame <- survey_df_1step
class(commonClasses$data_frame)
```

##4.2.5
```{r}
commonClasses$matrix <- matrix(
  c(2, 11, -1, 3, 4, -5), nrow=2, 
  byrow = T # default is by column
)
class(commonClasses$matrix)
```

```{r}
# non atomic matrix
matrix_nonAtomic <- matrix(
  list(
    32, "John", 
    33, "Jane", 
    34, "Ben"
    ), nrow=2
)
matrix_nonAtomic
```

If you already bind the source vector of matrix to a name, say x, you can simply change x’s dimension to convert it into matrix:
```{r}
x <- c(2, 11, -1, 3, 4, -5)
dim(x)
dim(x) <- c(2, 3)
```

```{r}
x[2, 1] # the same as
x[2]

x[2, c(2, 3)] # the same as
x[c(4, 6)]
```

```{r}
matrix_nonAtomic
matrix_nonAtomic[2, 1] # the same as 
matrix_nonAtomic[2]

matrix_nonAtomic[2, c(2, 3)] # the same as
matrix_nonAtomic[c(4, 6)]
```

```{r}
matrix_nonAtomic
matrix_nonAtomic[2, 1] # the same as 
matrix_nonAtomic[2]

matrix_nonAtomic[2, c(2, 3)] # the same as
matrix_nonAtomic[c(4, 6)]
```









